Estimating the distribution of block sizes as a function of average transaction rates

### 2015-10-20 paper/paper.tex
Added intro, new file

\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{bm, bbm}
%\usepackage{mathtools}

\author{Matt Simpson}
\title{Outline of Ideas for BTC Transaction Frequency}
\begin{document}
\maketitle

@@

>>>>

\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{bm, bbm}
%\usepackage{mathtools}
\usepackage[noblocks]{authblk}

\author[1]{Matt Simpson}
\author[2]{Eli Dourado}
\affil[1]{M. Simpson is a postdoctoral fellow in statistics at the University of Missouri}
\affil[2]{E. Dourado is a research fellow at the Mercatus Center at George Mason University and director of its Technology Policy Program, as well as a doctoral candidate in economics at George Mason University}
\title{Estimating the distribution of block sizes as a function of average transaction rates}
\renewcommand\Authand{, }
\begin{document}
\maketitle

@@

\section{Introduction}
The optimal maximum size of Bitcoin blocks is an area of active controversy. When the maximum size is set at a high level, mining centralization will increase due to higher resource demands, and the network becomes vulnerable to selfish mining attacks.\footnote{http://arxiv.org/abs/1311.0243} When the maximum size is too small, there is inadequate space to accommodate the volume of transactions that users demand, resulting in higher fees, wait times, and potentially lower rates of adoption, which affects security through the price of Bitcoin. The issue may be with us for some time; even assuming that current disagreements over raising the 1MB cap are resolved, if the Bitcoin network keeps growing and as computing power increases, the issue will need to be re-litigated from time to time. One proposal, BIP 100, would subject the decision to a continuous voting process by miners indefinitely into the future.

A better understanding of the relationship between the rate of Bitcoin transactions and block sizes is needed to inform this debate. Bitcoin blocks are discovered according to a Poisson process, directly implying that times between block discoveries are distributed exponentially. If transaction rates (in bytes per second) were constant, this would imply that block sizes too would be distributed exponentially. As the exponential distribution is well understood and has a closed-form cumulative density function, it would be trivial to evaluate the probability of blocks filling up as a function of the average transaction rate.

In fact, transaction rates are not constant. Block sizes are therefore not distributed exponentially, but according to some other distribution. In this paper, we empirically estimate the distribution of block sizes and calculate the probability that a block will reach the upper bound as a function of the average transaction rate. We find that the actual distribution of transaction data is more likely to result in a binding maximum than an exponential distribution would across the spectrum of average transaction rates, although the biggest effect is at the relatively low end.
